Adaptive Scheduling of Scientific Workflows\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-05-05 main.tex
unified the model

    \skug{TODO:unify the notation with the table!!}

    For a task~$u\in V$, we have a memory usage~$m_u$ and execution time~$w_u$.
    For an edge $(u,v)\in E$, we have a data of size $c_{u,v}$.

    For each processor $P_j$, we have a speed~$s_j$, and also two memory bounds:
    $\MM_j$ the processor memory, and $\MC_j$, the size of the communication buffer.
    We can decide to evict some data from the main memory if we are sending the data
    to another processor; it then stays in the communication buffer until it has been sent.

    We keep track of the current ready time of each processor and each communication
    channel, $\rt_j$ and $\rt_{j,j'}$, for all processors~$(j,j')$. Initially, all the ready times
    are set to~$0$.

    We also keep track of the currently available memory, $availM_j$ and $availC_j$,
    on respectively the processor memory and communication buffer.
    Furthermore, $\PD_j$ is a priority queue with the {\em pending data}
    that are in the memory of size $\MM_j$ but may be evicted to be communicated, if
    more memory is needed on~$p_j$. They are ordered by non-decreasing size.
    They correspond to some $c_{u,v}$'s.

    \begin{table}[h]
        \begin{center}
            \begin{tabular}{rl}
                \hline
                \textbf{Symbol}                       & \textbf{Meaning}                                         \\
                \hline
                $G = (V, E)$                          & Workflow graph, set of vertices (tasks) and edges        \\
                $\parents{u}$, $\children{u}$         & Parents of a task $u$, children of a task $u$            \\
                $m_u$                                 & Memory weight of task $u$                                \\
                $w_u$                                 & Workload of task $u$  (normalized execution time)          \\
                $c_{u,v}$                             & Communication volume along the edge $(u,v)\in E$         \\
                $F$, $\mathcal{F}$                    & A partitioning function and the partition it creates     \\
                $V_i$                                 & Block number $i$                                         \\ %\wrt~some $F$   \\
                $\cluster$, $k$                    & Computing system and its number of processors           \\
                $p_j$, proc($V_i$)                          & Processor number $j$, processor of block $V_i$                 \\
                $M_j$, $s_j$                               & Memory size and speed of processor $p_j$                          \\
                $\beta$                     & Bandwidth in the compute system                                \\
                $\bottomlevel{u}$                      & Bottom weight of task $u$ \\
                $\mu_G$, $\mu_i$ & Makespan of the entire workflow $G$ and of a block $V_i$               \\
                $\Gamma = (\mathcal{V}, \mathcal{E})$                      & Quotient graph, its vertices and its edges        \\
                $r_u$, $r_{V_i}$                            & Memory requirement of task $u$ and of block $V_i$                 \\
                $r_{\max}$                       & Maximum memory requirement in a workflow                              \\
                $\criticalpath$                       & Critical path in a workflow                              \\
                \hline
            \end{tabular}
        \end{center}
        \caption{Notation.} \label{tabnotation}
    \end{table}

>>>>

    We first describe the target applications, which are (large scientific) workflows,
    in Section~\ref{sec.mod.work}.  Next, we define the execution
    environment, a heterogeneous system (in terms of processor speed and memory size),
    in Section~\ref{sec.mod.plat}.

    \subsection{Workflow}
    \label{sec.mod.work}
    A workflow is modeled as a directed acyclic graph $G=(V, E)$, where $V$ is the set of vertices (tasks), and
    $E$ is a set of directed edges of the form $e=(u,v)$, with $u,v\in V$, expressing precedence constraints between tasks.
    Each task~$u \in V$  is performing $w_u$ operations, and it also
    requires some amount of memory to be executed, denoted as~$m_u$.
    Each edge $e=(u,v) \in E$ has a cost~$c_{u,v}$ that corresponds to the size of the output file written by task~$u$ and used as input by task~$v$.

    Hence, the total  memory requirement for the execution of task~$u$ consists of the input files
    (size of the files to be received from the parents),
    the output files (size of the files to be sent to the children),
    and the memory size~$m_u$:
    \[
        r_u = m_u + \sum_{v:(v,u)\in E}c_{v,u} + \sum_{v:(u,v)\in E} c_{u,v}.
    \]

    The parents of a task~$u\in V$ are the directly preceding tasks that must be completed before $u$ can be started, i.e., the set of parents is
    $ \parents{u} = \{v \in V: (v,u) \in E\}$. A task without parents is called a {\it source task}.
    The children tasks of~$u$ are the tasks following~$u$ directly according to the precedence constraints, i.e.,
    $ \children{u} = \{v \in V: (u,v) \in E\}$. A task without children is called a {\it target task}.
    Each task may have multiple parents and children.

    \subsection{Execution environment}
    \label{sec.mod.plat}

    The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
    consists of $k$ processors $p_1, \dots, p_k$.
    Each processor $p_j$ ($1 \leq j \leq k$) has an individual memory size $M_j$, a communication
    buffer size $MC_j$ and a speed~$s_j$.
    We can decide to evict some data from the main memory if we are sending the data
    to another processor; it then stays in the communication buffer until it has been sent.
    The execution time of a single task~$u\in V$ on a processor~$p_j$ is expressed as $\frac{w_u}{s_j}$.
    We assume that all processors are connected with the same bandwidth~$\beta$.

    We keep track of the current ready time of each processor and each communication
    channel, $\rt_j$ and $\rt_{j,j'}$, for all processors~$(j,j')$.
    Initially, all the ready times are set to~$0$.
    We also keep track of the currently available memory, $availM_j$ and $availC_j$,
    on respectively the processor memory and communication buffer.
    Furthermore, $\PD_j$ is a priority queue with the {\em pending data}
    that are in the memory of size $\MM_j$ but may be evicted to be communicated, if
    more memory is needed on~$p_j$. They are ordered by non-decreasing size.
    They correspond to some $c_{u,v}$'s.

    We use the \algo{memDag} algorithm from~\cite{KAYAASLAN20181} to compute
    the memory requirement by transforming the workflow into a series-parallel graph,
    and then finding the traversal that leads to the minimum memory consumption.

    \begin{table}[h]
        \begin{center}
            \begin{tabular}{rl}
                \hline
                \textbf{Symbol}                       & \textbf{Meaning}                                         \\
                \hline
                $G = (V, E)$                          & Workflow graph, set of vertices (tasks) and edges        \\
                $\parents{u}$, $\children{u}$         & Parents of a task $u$, children of a task $u$            \\
                $m_u$                                 & Memory weight of task $u$                                \\
                $w_u$                                 & Workload of task $u$  (normalized execution time)          \\
                $c_{u,v}$                             & Communication volume along the edge $(u,v)\in E$         \\
                $F$, $\mathcal{F}$                    & A partitioning function and the partition it creates     \\
                $V_i$                                 & Block number $i$                                         \\ %\wrt~some $F$   \\
                $\cluster$, $k$                    & Computing system and its number of processors           \\
                $p_j$, proc($V_i$)                          & Processor number $j$, processor of block $V_i$                 \\
                $M_j$, $MC_j$, $s_j$                               & Memory size, comm. buffer and speed of processor $p_j$                          \\
                $\beta$                     & Bandwidth in the compute system                                \\
                $\bottomlevel{u}$                      & Bottom weight of task $u$ \\
                $\mu_G$, $\mu_i$ & Makespan of the entire workflow $G$ and of a block $V_i$               \\
                $\Gamma = (\mathcal{V}, \mathcal{E})$                      & Quotient graph, its vertices and its edges        \\
                $r_u$, $r_{V_i}$                            & Memory requirement of task $u$ and of block $V_i$                 \\
                \hline
            \end{tabular}
        \end{center}
        \caption{Notation.} \label{tabnotation}
    \end{table}
